Secure Composition of Robust and Optimising Compilers

### 2023-06-13 popl/main.tex
Add todo
Minor patching to 1st contrib

\BrText{Solution}{
% keyword: pass
\MPin{
	commands missing
}
This paper introduces a framework for reasoning about the composition of secure and optimising compiler passes and it showcases the power of this framework by instantiating it on a multi-pass compilation chain.
To this end, this paper first discusses how to compose security properties, such as temporal and spatial memory safety into general memory safety, and cryptographic constant time.
Then, this paper defines several secure compiler passes, where each is either preserving a different security property (e.g., temporal or spatial memory safety) or performing a security-preserving optimisation, (e.g., applying constant-folding or dead-code elimination).
% keyword- end to end, composition
Finally, this paper shows how to compose these secure compiler passes into a multi-pass compilation chain which can be proven to provide end-to-end preservation of general memory safety and cryptographic constant time.
\MKin{
  ,,can be proven'' -> we prove (?)
}
Crucially, this end-to-end security preservation is obtained by having each compilation pass (i) preserve a sub-part of the overall security property individually and then (ii) compose each preserved security property as dictated by our framework.
Our results showcase how our framework allows the kind of formal security reasoning that compiler writers already want (and do), obtaining precise, compositional security reasoning while providing minimal (and modular) proof effort.
\MPin{
	last line: not the best.
}
}

@@

\begin{itemize}
  \item
        \Cref{sec:compprop} presents a formal framework to reason about compositions of security properties and demonstrate its usage with concrete examples:
        Given a most general trace model, we define the trace-based security properties \gls{tms}, \gls{sms}, \gls{ms}, \gls{cct}, and their compositions.
        For each of these properties, we also give a monitor which runs on another trace model that excludes unneccessary information and show that their composition is behaviorally similar to the composition of the trace-based security properties.
        This two-level approach enhances modularity: When working with the security properties, one only needs to reason about the corresponding monitor.

@@

>>>>

\BrText{Solution}{
% keyword: pass
\MPin{
	commands missing
}
This paper introduces a framework for reasoning about the composition of secure and optimising compiler passes and it showcases the power of this framework by instantiating it on a multi-pass compilation chain.
To this end, this paper first discusses how to compose security properties, such as temporal and spatial memory safety into general memory safety, and cryptographic constant time.
Then, this paper defines several secure compiler passes, where each is either preserving a different security property (e.g., temporal or spatial memory safety) or performing a security-preserving optimisation, (e.g., applying constant-folding or dead-code elimination).
% keyword- end to end, composition
Finally, this paper shows how to compose these secure compiler passes into a multi-pass compilation chain which can be proven to provide end-to-end preservation of general memory safety and cryptographic constant time.
\MKin{
  ,,can be proven'' -> is proven (?)
}
Crucially, this end-to-end security preservation is obtained by having each compilation pass (i) preserve a sub-part of the overall security property individually and then (ii) compose each preserved security property as dictated by our framework.
Our results showcase how our framework allows the kind of formal security reasoning that compiler writers already want (and do), obtaining precise, compositional security reasoning while providing minimal (and modular) proof effort.
\MPin{
	last line: not the best.
}
}

@@

\begin{itemize}
  \item %
        %\Cref{sec:compprop} presents a formal framework to reason about compositions of security properties and demonstrate its usage with concrete examples:
        A formal framework to reason about the composition of security properties (\Cref{sec:compprop}).
        %Given a most general trace model, we define the trace-based security properties \gls{tms}, \gls{sms}, \gls{ms}, \gls{cct}, and their compositions.
        Using the framework, the ease for formal reasoning about security property compositions is demonstrated by instantiating it on \gls{tms}, \gls{sms}, and \gls{cct}, which are ultimately composed to \gls{ms} and a combination of \gls{ms} and \gls{cct}.
        %For each of these properties, we also give a monitor which runs on another trace model that excludes unneccessary information and show that their composition is behaviorally similar to the composition of the trace-based security properties.
        %This two-level approach enhances modularity: When working with the security properties, one only needs to reason about the corresponding monitor.
        %%% let's omit above sentences completely. why ramble about monitors in the introduction? this ain't about model checking

@@

\MKin{combined version of all monitors? maybe just as lemma}
